Interactive Visualization for System Log Analysis

### 2013-12-18 paper/paper.tex
Fix typos

With a large enough cluster, this will require focusing the user’s attention on “interesting” parts
of the system state. This will require detecting anomalies, which in turn requires a
constantly-evolving model of what the “normal” state of the system is.

@@

Munin, based on RRDtool, is similar to Ganglia: after installation on each node, it automatically presents a visualization of the system status~\cite{Oetiker99}.
As is evident from Figure~\ref{fig:rrdtool}, the visualizations is extremely dense and illegible as the number of nodes increase.

@@

\begin{enumerate}
    \item Compute per-node features
    \item Perform distributed k-means clustering
    \item Display interactive visualization
\end{enumerate}

@@

\subsection{Clustering}
We perform k-means clustering in the feature vector space~\cite{kmeans,Lloyd82}.
With a small number of nodes (on the order of tens), the clustering can be performed on a single machine quickly.
On more nodes, a distributed $k$-means algorithm is required, which can either be exact~\cite{jin2006fast} or approximate and slower~\cite{kanungo2002local}.
Since the clustering will occur each time the user updates the parameters of the visualization, it is essential that it is fast.

Once the desired number of centroids are found, we compute the node which is closest to the centroid in a least-squares sense and display only that node.
Therefore, thhe visualization master server need only receive $O(k)$ data to pass on to the user, linear with the number of centroids, instead of with the total number of nodes.

@@

\subsection{Anomaly Detection}
\label{subsec:results:anomaly}
The metric of success for anomaly detection is as follow: assuming only one node is anomalous, how many clusters are required until that node is in its own cluster?
The best-case scenario is two clusters: one for each of the $n-1$ well-performing nodes, and another for the anomalous node.

@@

Only one out of every hundred messages is real. One node is still 5\% slower. Can the anomalous node be detected? Note that the filesize here is bloated to 100 times the actual log data.
\end{enumerate}

@@

We would like to eventually compare our algorithm with the results of Xu and collaborators \cite{Xu09}.
Unfortunately, all of their results used private proprietary logs, so we could not do a direct comparison.

@@

Figure~\ref{fig:timings} shows basic timing information of our system.
From this, it is clear that the per-node cost is small: less than two seconds to compute features per-node.
This data is then passed on to the master node, which preprocesses everything and prepares to send it to the client via HTTP.
This preprocessing is the bottleneck in our unoptimized implementation.
Finally, when the user changes the parameters with the web interface, the k-means clustering is recomputed at interactive rates.

When the number of nodes increases to 100, and the number of log messages to 50 million, we are still able to run the clustering in 2.1 seconds on a single thread.
We have not found it necessary to use distributed or approximate k-means clustering, but if the number of nodes increases, it will be worthwhile to use a sublinear k-means algorithm.

>>>>

With a large enough cluster, this will require focusing the user's attention on “interesting” parts
of the system state. This will require detecting anomalies, which in turn requires a
constantly-evolving model of what the “normal” state of the system is.

@@

Munin, based on RRDtool, is similar to Ganglia: after installation on each node, it automatically presents a visualization of the system status~\cite{Oetiker99}.
As is evident from Figure~\ref{fig:rrdtool}, the visualization is extremely dense and illegible as the number of nodes increases.

@@

\begin{enumerate}
    \item Compute per-node features
    \item Perform $k$-means clustering
    \item Display interactive visualization
\end{enumerate}

@@

\subsection{Clustering}
We perform $k$-means clustering in the feature vector space~\cite{kmeans,Lloyd82}.
With a small number of nodes (on the order of tens), the clustering can be performed on a single machine quickly.
On more nodes, a distributed $k$-means algorithm is required, which can either be exact and slower~\cite{jin2006fast} or approximate~\cite{kanungo2002local}.
Since the clustering will occur each time the user updates the parameters of the visualization, it is essential that it is fast.

Once the desired number of centroids are found, we compute the node which is closest to the centroid in a least-squares sense and display only that node.
Therefore, the visualization master server need only receive $O(k)$ data to pass on to the user, linear with the number of centroids, instead of with the total number of nodes.

@@

\subsection{Anomaly Detection}
\label{subsec:results:anomaly}
The metric of success for anomaly detection is as follows: assuming only one node is anomalous, how many clusters are required until that node is in its own cluster?
The best-case scenario is two clusters: one for each of the $n-1$ well-performing nodes, and another for the anomalous node.

@@

Only one out of every hundred messages is real. One node is still 5\% slower. Can the anomalous node be detected? Note that the file size here is bloated to 100 times the actual log data.
\end{enumerate}

@@

We would like to eventually compare our algorithm with the results of Xu and collaborators \cite{Xu09}.
Unfortunately, all of their results used private and proprietary logs, so we could not do a direct comparison.

@@

Figure~\ref{fig:timings} shows basic timing information of our system.
From this, it is clear that the per-node cost is small: less than two seconds to compute features per-node.
This preprocessing is the bottleneck in our unoptimized implementation.
After the distributed preprocessing this data is then passed on to the master node, which prepares to send it to the client via HTTP.
Finally, when the user changes the parameters with the web interface, the $k$-means clustering is recomputed at interactive rates.

When the number of nodes increases to 100, and the number of log messages to 50 million, we are still able to run the clustering in 2.1 seconds on a single thread.
We have not found it necessary to use distributed or approximate $k$-means clustering, but if the number of nodes increases, it will be worthwhile to use a sublinear $k$-means algorithm.
